Supplementary Information

### 2021-01-12 doc/manuscript/MEE_manuscript.Rmd
Update MEE_manuscript.Rmd
#108

```{r , eval=FALSE, echo=FALSE}
## Tallies for the following paragraph (Jan 6)
#sameV_sameW: LDWp, NMt,NMp, NIOt, NIOp, SCBIp,  ZOFp,ZOFt,  (8)
#sameV_diffW: BCNMp, BCNMt, HFt, HKKp, LDWt,  SCBIt, SCp,SCt,  CBp, CBt (10)
#diffV_diffW: HFp, HKKt
```
The three metrics of growth ($RW$, $BAI$, and $\Delta AGB$)  exhibited similar strength of correlation and direction of response to climate variables across the range of potential time windows, but the optimal time window or even the top climate variable sometimes differed (Figs. `r all_climwin`).
In 8 of 20 cases, both the optimal climate variable and time window were identical across growth metrics (e.g., Fig. `r climwin_sameV_sameW`). 
In 10 cases, *climwin* identified the same climate variable but different (often overlapping) time windows (e.g., Fig. `r climwin_sameV_diffW`). 
Finally, in two cases of variables that had only weak effects and mixed responses among species in the final models (temperature variable group at HKK, precipitation variable group at HF; Figs. `r clim_sens`, `r GLS_HKK`, `r GLS_HF`), *climwin* identified different climate variables and different time windows (e.g., Fig. `r climwin_diffV_diffW`). 
Henceforth, unless otherwise noted, we focus on the climate sensitivities identified with $RW$ as the growth metric and for the full set of cores (*i.e.*, including those for which $DBH$ could not be reconstructed).

```{r , eval=FALSE, echo=FALSE}
## Tallies for the paragraph below (as of Jan 6)
#BCNM: 1 species with both, 2 with just P
#HKK: 3 species with both, 1 with just T
#SCBI: 11 species with both, 3 with just P (FRNI, FAGR, PIST)
#LDW:  4 species with both,  2  with just P
#HF:  4 species with both
#ZOF:  3 species with both
#NIO:  1 species with both
#LT:  2 species with both
#CB:  7 species with both,  1 with just P (PILO)
#SC:  1 species with both
```
Within the context of the GLS model, which tested for first- and negative second- order linear effects of both a precipitation and a temperature variable, both a precipitation and a temperature variable were included in the top model for 80% of site-species combinations (n=37 of 46; Fig. `r clim_sens`). 
There were eight site-species combinations for which only a precipitation term was significant (2 at BCNM, 3 at SCBI, 2 at LDW, and 1 at CB), one for which only a temperature term was significant (CHTA at HKK), and none with no significant climate responses. 
Precipitation and temperature variables were rarely influential over the same time window (exception: LDW).
Below, we summarize the precipitation and temperature variables included in these models and their direction of response.

>>>>

```{r , eval=FALSE, echo=FALSE}
## Tallies for the following paragraph (Jan 12)
#sameV_sameW: LDWp, NMt,NMp, NIOt, NIOp, SCBIp,  ZOFp,ZOFt,  (8)
#sameV_diffW: BCNMp, BCNMt, HFt, HKKp, LDWt,  SCBIt, SCp,SCt,  CBp, CBt (10)
#diffV_diffW: HFp, HKKt
```
The three metrics of growth ($RW$, $BAI$, and $\Delta AGB$)  exhibited similar strength of correlation and direction of response to climate variables across the range of potential time windows, but the optimal time window or even the top climate variable sometimes differed (Figs. `r all_climwin`).
In 8 of 20 cases, both the optimal climate variable and time window were identical across growth metrics (e.g., Fig. `r climwin_sameV_sameW`). 
In 10 cases, *climwin* identified the same climate variable but different (often overlapping) time windows (e.g., Fig. `r climwin_sameV_diffW`). 
Finally, in two cases of variables that had only weak effects and mixed responses among species in the final models (temperature variable group at HKK, precipitation variable group at HF; Figs. `r clim_sens`, `r GLS_HKK`, `r GLS_HF`), *climwin* identified different climate variables and different time windows (e.g., Fig. `r climwin_diffV_diffW`). 
Henceforth, unless otherwise noted, we focus on the climate sensitivities identified with $RW$ as the growth metric and for the full set of cores (*i.e.*, including those for which $DBH$ could not be reconstructed).

```{r , eval=FALSE, echo=FALSE}
## Tallies for the paragraph below (as of Jan 12)
#BCNM: 1 species with both, 2 with just P
#HKK: 3 species with both, 1 with just T (CHTA)
#SCBI: 11 species with both, 3 with just P (FRNI, FAGR, PIST)
#LDW:  4 species with both,  2  with just P (ACSA, CAOV)
#HF:  4 species with both
#ZOF:  3 species with both
#NIO:  1 species with both
#LT:  2 species with both
#CB:  8 species with both
#SC:  1 species with both
```
Within the context of the GLS model, which tested for first- and negative second- order linear effects of both a precipitation and a temperature variable, both a precipitation and a temperature variable were included in the top model for 80% of site-species combinations (n=37 of 46; Fig. `r clim_sens`). 
There were seven site-species combinations for which only a precipitation term was significant (2 at BCNM, 3 at SCBI, and 2 at LDW), one for which only a temperature term was significant (*Chukrasia tabularis* at HKK), and none with no significant climate responses. 
Precipitation and temperature variables were rarely influential over the same time window (exception: LDW).
Below, we summarize the precipitation and temperature variables included in these models and their direction of response.
